PubCrawl: A Publication Search Engine

### 2012-05-17 report/paper.tex
Fix preamble
Set margins, and include a macro for rendering "SiteSeerX"
Remove unnecessary notation

\usepackage{graphicx}

@@

\begin{abstract}
Searching for documents ranked by relevance is a well-studied problem for web
pages. In particular, there are frameworks for estimating relevance as a
function of the content of the document and algorithms for estimating relevance
as a function of incoming links. However, further specialization of these
techniques is required to search a corpus of academic papers. Academic papers
are highly structured, lending additional weight to matches which appear in
important sections such as the title or abstract. Moreover, citations have
contextual information which changes the weight which should be contributed to
cited papers. Here we describe PubCrawl, a search engine built for the ACM
Digital Library. The system allows users to weight the relative importance of
matches in various sections of the documents. We also implement a version of
PageRank over the dataset. We evaluate the system in user studies.
\end{abstract}

@@

Lucene uses the Boolean model \cite{lancaster73} to filter documents and the
Vector Space Model \cite{salton75} to score documents. Documents $d$ and
queries $q$ are vectors $V(\cdot)$ with each term a dimension and coordinates
equal to tf*idf values. Then, the relevance of a document to a query is related
to the angle between them (the cosine similarity score). Lucene generalizes the
cosine similarity score in several ways. First, documents are allowed to have
multiple and duplicate fields. Second, Lucene allows index-time boosting of
documents and fields as well as query-time boosting of query terms. Finally,
Lucene does not require every term to appear in hits, instead using a
coordination factor to score documents which contain more terms higher. These
features can be exploited to improve the quality of search results.

>>>>

\usepackage{graphicx}
\usepackage[letterpaper,margin=1in]{geometry}

\newcommand{\citeseer}{CiteSeer$^\chi$}

@@

\begin{abstract}
Searching for documents ranked by relevance is a well-studied problem in
information retrieval. In particular, there are frameworks for estimating
relevance as a function of the content of the document and algorithms for
estimating relevance as a function of incoming links. However, further
specialization of these techniques is required to search a corpus of academic
papers. Academic papers are highly structured, lending additional weight to
matches which appear in important sections such as the title or abstract.
Contextual information changes the weight which should be contributed to cited
papers. Here we describe PubCrawl, a search engine built for the ACM Digital
Library. The system allows users to weight the relative importance of matches
in various sections of the documents. We also implement a version of PageRank
over the dataset. We evaluate the system in user studies.
\end{abstract}

@@

Lucene uses the Boolean model \cite{lancaster73} to filter documents and the
Vector Space Model \cite{salton75} to score documents. Documents and queries
are vectors with each term a dimension and coordinates equal to tf*idf values.
Then, the relevance of a document to a query is related to the angle between
them (the cosine similarity score). Lucene generalizes the cosine similarity
score in several ways. First, documents are allowed to have multiple and
duplicate fields. Second, Lucene allows index-time boosting of documents and
fields as well as query-time boosting of query terms. Finally, Lucene does not
require every term to appear in hits, instead using a coordination factor to
score documents which contain more terms higher. These features can be
exploited to improve the quality of search results.
